\LARGE \bf Multi-dimensional Optimization of Gasoline-fueled Variable Pitch Multirotor Aircraft

### 2016-03-23 paper.tex
some small changes
Updated intro

@@

\author{Daillin Briggs, Gary Ellingson% <-this % stops a space
%\thanks{$^{1}$James Jackson is a MS student in the Department of Mechanical Engineering, Brigham Young University
%        {\tt\small jamesjackson@byu.edu}}%
%\thanks{$^{2}$Gary Ellingson is a MS student in the Department of Mechanical Engineering, Brigham Young University
%        {\tt\small gary.ellingson@byu.edu}}%
}

@@

This paper looks at the why and how we are going to optimize a multirotor platform to maximize flight time

@@

(Will talk more about some of the details this entails in the paper).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{METHODS}
analysis models

Empirical engine models
aerodynamic models
Simplifications - we are stupid

\section{OPTIMIZATION}
Setup the formal optimization problems

What optimizers, setup, comparing matlab and python. 
figure of Pareto fronts...

@@

>>>>

\newcommand{\vect}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\mat}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\transpose}{\ensuremath{\mathsf{T}}}
\newcommand{\of}[1]{\ensuremath{\left(#1\right)}}

@@

\author{Dallin Briggs, Gary Ellingson% <-this % stops a space
%\thanks{$^{1}$James Jackson is a MS student in the Department of Mechanical Engineering, Brigham Young University
%        {\tt\small jamesjackson@byu.edu}}%
%\thanks{$^{2}$Gary Ellingson is a MS student in the Department of Mechanical Engineering, Brigham Young University
%        {\tt\small gary.ellingson@byu.edu}}%
}

@@

\begin{itemize}
	\item{This paper looks at the why and how we are going to optimize a multirotor platform to maximize flight time.}
	\item{Talk about how the variables that are going to be optimized are rotor radius, fuel consumption rate, number of blade per rotor, number of rotors, rotor speed, and rotor pitch.}
	\item{Talk about why these variables were selected as design variables.}
	\item{Talk about some physical constraints, especially those imposed by the FAA.}
\end{itemize}

@@

\begin{itemize}
	\item{Will talk more about some of the details using a gas engine entails in the paper.}
	\item{Speak briefly on the reasons for requiring variable pitch with a gas engine.} 
	\item{Speak on current platforms and capabilities and explain how this could fundamentally change the way multirotors are used in commercial applications, but not really for consumers.}
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{METHODS}

First model used in the beginning of the project was 
$$t_{flight} = \frac{E_{cap} \eta_{engine}}{n_{rotors}P_{adj}},$$

\begin{itemize}
	\item{Analysis models}
	\begin{itemize}
		\item{Empirical engine models}
		\item{Rotor Aerodynamic models}
	\end{itemize}
	\item{Simplifications - since we are stupid}
\end{itemize}

\section{OPTIMIZATION}
Setup the formal optimization problem
\begin{equation}
min. \quad f\of{x} = -flightTime\of{x}
\label{eq:objective}
\end{equation}
\begin{equation}
w.r.t. \quad x = [variables]^T
\label{eq:vars}
\end{equation}
\begin{equation}
s.t. \quad cons\of{x} <= 0 
\label{eq:constrants}
\end{equation}

What optimizers, setup, comparing matlab and python.

Figure of Pareto fronts...

@@

\section{RESULTS AND DISCUSSION}

\begin{itemize}
	\item{Table showing the optimal design parameters}
\end{itemize}
